---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
<!-- badges: end -->

# Overview

**SNMoE** (Skew-Normal Mixtures-of-Experts) provides a flexible modelling 
framework for heterogenous data with possibly skewed distributions to 
generalize the standard Normal mixture of expert model. **SNMoE** consists of 
a mixture of *K* skew-Normal expert regressors network (of degree *p*) gated by
a softmax gating network (of degree *q*) and is represented by:

* The gating network parameters `alpha`'s of the softmax net.
* The experts network parameters: The location parameters (regression 
coefficients) `beta`'s, scale parameters `sigma`'s, and the skewness 
parameters `lambda`'s. **SNMoE** thus generalises mixtures of (normal, 
skew-normal) distributions and mixtures of regressions with these 
distributions. For example, when $q=0$, we retrieve mixtures of (skew-normal, 
or normal) regressions, and when both $p=0$ and $q=0$, it is a mixture of 
(skew-normal, or normal) distributions. It also reduces to the standard 
(normal, skew-normal) distribution when we only use a single expert ($K=1$).

Model estimation/learning is performed by a dedicated expectation conditional 
maximization (ECM) algorithm by maximizing the observed data log-likelihood. 
We provide simulated examples to illustrate the use of the model in 
model-based clustering of heterogeneous regression data and in fitting 
non-linear regression functions.

# Installation

You can install the development version of SNMoE from [GitHub](https://github.com/)
with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/SNMoE")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/SNMoE", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("SNMoE")
```

# Usage

```{r, message = FALSE}
library(SNMoE)
```

```{r, echo = TRUE}
# Application to a simulated data set

n <- 500 # Size of the sample
alphak <- matrix(c(0, 8), ncol = 1) # Parameters of the gating network
betak <- matrix(c(0, -2.5, 0, 2.5), ncol = 2) # Regression coefficients of the experts
lambdak <- c(3, 5) # Skewness parameters of the experts
sigmak <- c(1, 1) # Standard deviations of the experts
x <- seq.int(from = -1, to = 1, length.out = n) # Inputs (predictors)

# Generate sample of size n
sample <- sampleUnivSNMoE(alphak = alphak, betak = betak, sigmak = sigmak, 
                          lambdak = lambdak, x = x)
y <- sample$y

K <- 2 # Number of regressors/experts
p <- 1 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE
verbose_IRLS <- FALSE

snmoe <- emSNMoE(X = x, Y = y, K, p, q, n_tries, max_iter, 
                 threshold, verbose, verbose_IRLS)

snmoe$plot()
```

```{r, echo = TRUE}
# Application to a real data set

data("tempanomalies")
x <- tempanomalies$Year
y <- tempanomalies$AnnualAnomaly

K <- 2 # Number of regressors/experts
p <- 1 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE
verbose_IRLS <- FALSE

snmoe <- emSNMoE(X = x, Y = y, K, p, q, n_tries, max_iter, 
                 threshold, verbose, verbose_IRLS)

snmoe$plot()
```
