---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
<!-- badges: end -->

# Overview

User-friendly and flexible algorithm for modeling, sampling, inference, and 
clustering heteregenous data with the Skew-Normal Mixture-of-Experts (SNMoE) 
model.

# Installation

You can install the development version of SNMoE from [GitHub](https://github.com/)
with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/SNMoE")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/SNMoE", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("SNMoE")
```

# Usage

```{r, message = FALSE}
library(SNMoE)
```

```{r, echo = TRUE}
n <- 500 # Size of the sample
K <- 2 # Number of regressors/experts
p <- 1 # Order of the polynomial regression (regressors/experts)
q <- 1 # Order of the logistic regression (gating network)

alphak <- matrix(c(0, 8), ncol = K - 1) # Parameters of the gating network
betak <- matrix(c(0, -2.5, 0, 2.5), ncol = K) # Regression coefficients of the experts
lambdak <- c(3, 5) # Skewness parameters of the experts
sigmak <- c(1, 1) # Standard deviations of the experts
x <- seq.int(from = -1, to = 1, length.out = n) # Inputs (predictors)

# Generate sample of size n
sample <- sampleUnivSNMoE(alphak = alphak, betak = betak, sigmak = sigmak, 
                          lambdak = lambdak, x = x)

n_tries <- 1
max_iter = 1500
threshold <- 1e-6
verbose <- TRUE
verbose_IRLS <- FALSE

snmoe <- emSNMoE(x, matrix(sample$y), K, p, q, n_tries, max_iter, 
                 threshold, verbose, verbose_IRLS)

snmoe$plot()
```
